---
title: "My Solution"
author: "Justin Sparto"
date: "2022-12-06"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Part 1
## Find Total Score based on strategy guide (input data)

###  Initialize DF
```{r}
df = read.table('./data/input.txt',sep='')

# Rename Cols
df <- df %>% 
  rename('them' = 'V1',
         'me' = 'V2')

# Add score col
df$my_score = 0

```

### Loop through df adding my_score
```{r}

for(i in 1:nrow(df)) {
  
  if (df$them[i] == 'A' && df$me[i] == 'X'){
    df$my_score[i] <- 4
  }
  else if (df$them[i] == 'B' && df$me[i] == 'Y'){
    df$my_score[i] <- 5
  }
  else if (df$them[i] == 'C' && df$me[i] == 'Z'){
    df$my_score[i] <- 6
  }
  else if (df$them[i] == 'A' && df$me[i] == 'Y'){
    df$my_score[i] <- 8
  }
  else if (df$them[i] == 'A' && df$me[i] == 'Z'){
    df$my_score[i] <- 3
  }
  else if (df$them[i] == 'B' && df$me[i] == 'X'){
    df$my_score[i] <- 1
  }
  else if (df$them[i] == 'B' && df$me[i] == 'Z'){
    df$my_score[i] <- 9
  }
  else if (df$them[i] == 'C' && df$me[i] == 'X'){
    df$my_score[i] <- 7
  }
  else if (df$them[i] == 'C' && df$me[i] == 'Y'){
    df$my_score[i] <- 2
  }
  else{
    print("Someone's a cheater")
  }
}
```


### Output total score
```{r}
df %>% 
    summarise(TotalScore = sum(my_score))
```

# Part 1 Complete
## Answer: My Score would be 13,565 if everything goes exactly according to the strategy guide!

# Part 2
## The guides meaning has changed slightly

```{r}
for(i in 1:nrow(df)) {
  
  if (df$them[i] == 'A' && df$me[i] == 'X'){
    df$my_score[i] <- 3
  }
  else if (df$them[i] == 'B' && df$me[i] == 'Y'){
    df$my_score[i] <- 5
  }
  else if (df$them[i] == 'C' && df$me[i] == 'Z'){
    df$my_score[i] <- 7
  }
  else if (df$them[i] == 'A' && df$me[i] == 'Y'){
    df$my_score[i] <- 4
  }
  else if (df$them[i] == 'A' && df$me[i] == 'Z'){
    df$my_score[i] <- 8
  }
  else if (df$them[i] == 'B' && df$me[i] == 'X'){
    df$my_score[i] <- 1
  }
  else if (df$them[i] == 'B' && df$me[i] == 'Z'){
    df$my_score[i] <- 9
  }
  else if (df$them[i] == 'C' && df$me[i] == 'X'){
    df$my_score[i] <- 2
  }
  else if (df$them[i] == 'C' && df$me[i] == 'Y'){
    df$my_score[i] <- 6
  }
  else{
    print("Someone's a cheater")
  }
}
```

```{r}
df %>% 
    summarise(TotalScore = sum(my_score))
```

# Part 2 Complete
## Answer: My Score would be 12,424 if everything goes exactly according to the strategy guide!



















