---
title: "My Solution"
author: "Justin Sparto"
date: "2022-12-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```


# Part 1
## Find the item type that appears in both compartments of each rucksack. What is the sum of the priorities of those item types?

###  Initialize DF
```{r}
df = read.table('./data/input.txt')

df2 <- df

```

```{r}
lowerLetters <- letters[1:26]

upperLetters <- LETTERS[1:26]

myLetters <- append(lowerLetters, upperLetters)

# match("A", myLetters) - # Outputs 27

```



### Loop through DF
```{r}

for (i in 1:nrow(df)){
  
  string <- df$V1[i]
  
  # Determine Length of string
  length <- nchar(string)
  
  # Parse string
  firstHalf <- substr(string, 1, length/2)
  
  secondHalf <- substr(string, length/2+1, length)
  
  # Add to DF
  df$V2[i] <- firstHalf
  df$V3[i] <- secondHalf
  
}

```



```{r}
# Finds common value and adds priority score to new col based
for (i in 1:nrow(df)){
  
  firstHalf <- unlist(strsplit(df$V2[i],""))
  secondHalf <- unlist(strsplit(df$V3[i],""))
  
  commonChar <- intersect(firstHalf, secondHalf)
  
  df$score[i] <- match(commonChar, myLetters)
}
```


```{r}
df %>%
  summarise(total = sum(score))

```

# Part 1 Complete
## After finding the item type that appears in both compartments of each rucksack, assigning a priority score and summing them... we get an answer of 7824.

# Part 2
## Find the item type that corresponds to the badges of each three-Elf group. What is the sum of the priorities of those item types?

```{r}

df3 <- data.frame(V1 = NA, V2 = NA, V3 = NA)

i <- 1

while (i <= nrow(df2)){
    
  string1 <- df2$V1[i]
  string2 <- df2$V1[i+1]
  string3 <- df2$V1[i+2]
    
  df3[nrow(df3)+1, 1] <- string1
  df3[nrow(df3), 2] <- string2
  df3[nrow(df3), 3] <- string3
 
  i <- i+3
}

df3 <- df3[-1,]
```


```{r}
for (i in 1:nrow(df3)){
  
  first <- unlist(strsplit(df3$V1[i],""))
  second <- unlist(strsplit(df3$V2[i],""))
  third <- unlist(strsplit(df3$V3[i],""))
  
  commonChar <- intersect(intersect(first, second), third)
  
  df3$score[i] <- match(commonChar, myLetters)
}
```


```{r}
df3 %>%
  summarise(total = sum(score))

```

# Part 2 Complete
## After Finding the item type that corresponds to thte badges of each of the three elves... the sum of the priorities of those items was 2,798


















